%        File: resume.tex
%      Author: Leon Zaruvinsky
%     License: MIT License
%     Created: Fri Sep 05 06:00 PM 2014 E
% Last Change: Fri Sep 05 12:40 AM 2014 E
%
%
% There are two additionally defined types of subsection headers:
%
% \subsectiond{Arg 1}{Arg 2}
% Arg 1 is left aligned, Arg 2 is tabbed from Arg 1
%
% \subsectionp{Arg 1}{Arg 2}{Arg 3}
% Arg 1 is left aligned, Arg 2 is tabbed from Arg 1, and Arg 3 is right aligned
%
% See the sample PDF for a visual 
%
% % % % % % % % % % %
%
% \desc = description, aka paragraph
%
% % % % % % % % % % %
%
% This is my first LaTeX document, so I don't expect it to be pretty or perfect.
% Rather, I haven't been able to find a Resume template I liked so I made my own.
%
% If you find any errors or want to make improvements, feel free to submit a pull request.
%
%

\documentclass{resume}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{enumitem}

\begin{document}
\pagenumbering{gobble}
\name{Crystal Fletcher}

\info{\href{mailto:tafletch@mtu.edu}{tafletch@mtu.edu}}{(989) 259-0273}{\href{https://www.linkedin.com/in/crystal-fletcher-639a3a170/}{linkedin.snreloaded.stream}}{\href{https://github.com/CrystalSpore}{GitHub.com/CrystalSpore}}

\vspace{-1.5em}
\section{Education}
\subsectionp{Michigan Technological University}{Houghton, MI}{Expected May 2020}
\desc{B.S. in Computer Science, Departmental GPA 3.58}

\subsection{Selected Coursework}
\hspace{12pt} \begin{tabularx}{\linewidth}{r X}
    In Progress & Programming Languages, Husky Game Development, \& Systems Programming \\
    Completed & Programming at the HW/SW Interface, Intro to Database Systems, Team Software Project, Formal Models of Computation, \& Computer Organization
\end{tabularx}

\vspace{-1em}

\section{Work Experience}

\subsectionp{Vertanen Research, VelociTap Text Auto-Correction}{Houghton, MI}{January 2017 - Present}
\desc{\begin{itemize}[leftmargin=*]
    \setlength\itemsep{-.1em}
    \item Development of experimental applications in text auto-correction and input stimuli.
    \item Use of Application Programming Interface (API) in development of Smartwatch testing app.
    \item Development within the research team accomplised both independently and as group programming.
\end{itemize}}

\subsectionp{MTU Computer Science Learning Center Coach}{Houghton, MI}{September 2017 - Present}
\desc{\begin{itemize}[leftmargin=*]
    \setlength\itemsep{-.1em}
    \item I tutor students on logic and problem solving skills relating to programming \& discrete math.
\end{itemize}}

\subsectionp{Lowe's Home Improvement Center}{Midland, MI}{Summers of  2017 \& 2018}
\desc{\begin{itemize}[leftmargin=*]
    \setlength\itemsep{-.1em}
    \item Started as Cashier, interfacing with customers.
    \item Promoted in summer 2018 to the Customer Service Desk, where I helped customers with problems.
\end{itemize}}

\section{Languages and Technologies}

\desc{
	\begin{description}
		\item[Most Experienced] Java, C/C++, HTML5/CSS3/XHTML, Git \& GitHub
		\item[Some Familiarity] Rust, JavaScript (Node.js), MySQL, Android, Assembly, C\#, \& \LaTeX
	\end{description}
}

\section{Side Projects}

\subsectionp{Personal Website: {\href{https://SNReloaded.stream}{SNReloaded.stream}}}{}{}
\desc{Self Hosted website with most everything hand coded. SSL certificate included for secure connection. Source: \href{https://github.com/CrystalSpore/SNReloaded.stream}{github.com/CrystalSpore/SNReloaded.stream}}

\subsectionp{ATOM (A Tiny Object Modeler)}{}{}
\desc{Project for the Team Software Project class. Source: \href{https://github.com/TSP-Molecule/ATOM}{github.com/TSP-Molecule/ATOM}}

\section{Extracurricular Activities}

\subsectionp{Copper County Coders - Mentoring}{}{September 2016 - May 2017}
\desc{Mentor middle school and high school students in various programming languages \& web design.}

\subsectionp{FIRST Robotics}{Team 2619}{October 2012 - August 2016}
\desc{Active member and programming lead, and team qualified for MI State \& Worlds competition all 4 years}

\end{document}
